\documentclass[10pt,a4paper,openany,oneside,onecolumn,titlepage]{report}
\usepackage[utf8]{inputenc}
\usepackage{amsmath}
\usepackage{amsfonts}
\usepackage{amssymb}
\usepackage{graphicx}
\usepackage[bookmarks]{hyperref}
\author{
        Talha Ahmed \\ Computer Graphics Researcher \and 
        Qurban Ali \\ CGI Pipeline Engineer
}
\title{ Pipeline Toolbox \\ ICE Animations }
\date{\today}
\setcounter{secnumdepth}{1}
\setcounter{tocdepth}{1}
\begin{document}
\maketitle
\tableofcontents \newpage
\chapter{Introduction}
This document describes the tools which developed and deployed by the Pipeline
Team at ICE Animations over the years.

The purpose of this document is to present a description of different software
available to the end user from the production team. This document can also be
used as a reference for learning what each tool in the menu does.

These pipeline tools have been developed and accumulated over the years by
different individuals since the inception of many projects. They have catered
to the workflow needs of many individuals working in many production projects.
We have limited amount of data as to how many times each tool has been used
during production. In this context, the evolution of this tool box in the near
future at least is heavily dependent on the feedback and requirements
communication apart from the capability of the development team. This document
should help the enduser of our pipeline tools to get an idea of what kind of
automations can be done, in order to suggest more ideas and improvements

The Pipeline team has produced and deployed broadly two different kind of
software for the production team. The first kind of software is what runs
inside Maya and other production software. The second kind of software runs in
the windows OS as standalone software. Both these kind of software have their
utility in different stages of the production pipeline.

The Pipeline team is responsible for maintaining and updating the tool box,
and our IT team takes care that all the software and data contained
within these toolboxes is backed up properly according to the needs of the
pipeline.

\input{TechnicalInfo.tex}

\chapter{ICE Menu - Toolbox Inside Autodesk Maya}
This Chapter describes the different custom tools available in Autodesk Maya
through a program menu. In order to install this menu when on the
ICEANIMATIONS intranet refer to the installation section
\ref{sec:installation}
All the available tools have been classified roughly according to the
department or pipeline stage they are most likely required in.

\input{MayaAnimation.tex}

\chapter{ICE Programs Menu}

This Chapter describes programs in the Pipeline Toolbox that run in the
windows OS outside but not necessarily independant of the production software.

\input{ExpoCache.tex}
\input{ExpoFast.tex}
\input{FrameChecker.tex}
\input{PaintDesk.tex}

\chapter{Conclusion}

The pipeline team at ICE Animations like in any other studio is essentially a
support center created to serve the production team in order to help them
organize and speed up their work through automation. The advantage and value
of an in-house developed tool is its conciseness and ability to tune it
towards the exact needs of the production team or individuals’ workflow. In
this context, the progress of the pipeline team directly depends upon the
quality and the quantity of ideas generated by individuals in the production
team and those communicated aptly to the development team. Also, the metrics
which define separate success from failure and the ones which measure progress
for this team are also determinable essentially from its contribution in
production.

A scan through of this document should enable the reader to gage
the kind of tools needed in our production pipeline, along with the capability
of the development team and also provide the basis for more creative thinking
which may lead towards ideas for development of more tools. The pipeline team
welcomes all such ideas for discussion and possible implementation.


\end{document}
